MSOA domestic Electricty and Gas maps

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Changing title

---
title: "Solent region: Test Maps"
author: "Meghan Kinglsey-Walsh"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---

>>>>

---
title: "MSOA domestic Electricty and Gas maps"
author: "Meghan Kinglsey-Walsh"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---
